A convenient, flexible and intuitive analytic expression for the metallicity-dependent cosmic star formation rate

### 2022-06-09 src/tex/ms.tex
[showyourwork] overleaf sync

We investigate the effect of the shape of the cosmic metallicity distribution on the local mass distribution of BBH mergers by systemically varying each of the variables that make up \dpdZ (first column of Table \ref{tab: fit params} and eq. \ref{eq: z log skew}).

>>>>

We will now demonstrate the flexibility of our analytical model by systematically varying each of the parameters in our fiducial \SFRDzZ model, and investigate their effect on the local mass distribution of BBH mergers originating from isolated binaries.   
To this end we use the publicly available rapid binary population synthesis simulations as presented in \cite{vanson+2022}. These simulations were run using version v02.19.04 of the open source \COMPAS suite \citep{COMPAS_method} \footnote{\url{https://github.com/TeamCOMPAS/COMPAS}}. \COMPAS is based on algorithms  model the evolution of massive stars in binary systems following \citet{Hurley+2000, Hurley+2002}, based on detailed evolutionary models by \citet{Pols+1998}.
We use the framework described in \cite{vanson+2022} to compute local merger rates of BBH systems.

% that is part of the \COMPAS suite 
% We investigate the effect of the shape of the cosmic metallicity distribution on the local mass distribution of BBH mergers by systemically varying each of the variables that make up \dpdZ (first column of Table \ref{tab: fit params} and eq. \ref{eq: z log skew}).
